---
title: "Day1 - Exercise 4 (SOLUTION)"
subtitle: "Example struma"
author: "YOUR NAME"
date: "`r Sys.Date()`"
output:
  word_document:
    reference_docx: templates/template_course_v20240227.docx
    toc: yes
    toc_depth: 2
    fig_width: 6.8
    fig_height: 4.2
---

```{r setup, include = FALSE}
# settings for output
  knitr::opts_chunk$set(echo = FALSE)


# Change setting of figure width and height
  knitr::opts_chunk$set(fig.width = ggplot2::unit(10, "cm"), fig.height = ggplot2::unit(8, "cm"))

# Change options such that progress bar is not shown in the output file <- NEW!!!
  knitr::opts_knit$set(progress = FALSE, verbose = TRUE)

# libraries used in this Rmd
  library(ggplot2)
  library(tidyverse)
  library(flextable)
  library(gtsummary)
  library(knitr)
  
  library(cowplot)
```

```{r,  echo = FALSE, eval = TRUE}
# Load Rdata file
  filename <- list.files(path = "../Rdata/", pattern = "struma_prepared")

 load(file = paste0("../Rdata/", filename))

# show general information about dataset

 info$general %>% 
   flextable::flextable() %>% 
   flextable::font(., fontname = "Cambria (Textkörper)", part = "all") %>%
      flextable::fontsize(., size = 10 , part = "all") %>%
      flextable::padding(padding.top = 0,
                         padding.bottom = 0, part = "body") %>% 
  
      flextable::hline(.,
              border = officer::fp_border(color = "grey70", style = "dotted")) %>%
      # flextable::align(., j = 1, part = "all") %>%
      flextable::bg(., bg = "grey90", part = "header") %>% 
      flextable::bold(., bold = TRUE, part = "header") %>% 
      flextable::autofit()  

```

We will use 'knit_child()' to call `subroutine` Rmd file.

**TO DO**

* Produce a report for struma data set with descriptive statistics
   - use knit_child()
      + create one 'subRmd' for categorical and another for continuous parameters
      + reuse solutions from exercise 2 
      + use for 'dt_struma' a placeholder 'dt_analysis'
   - use for loop to call the 'subRmd'
      + hint: one loop for categorical and one loop for continuous
* Optional
   - produce a docx file instead of a html output
      + hint: https://bookdown.org/yihui/rmarkdown/word-document.html
   - include your own docx template
      + hint: https://rmarkdown.rstudio.com/articles_docx.html


# Descriptive statistics

```{r}
# placeholders
dt_analysis <- dt_struma

group_int <- "MED"
group_int_lab <- "Medication"
group_int_colors <- c("#00AFBB", "#E7B800")

vec_var_int_categorical <- c("gender", "bloodgrp", "smoking")
vec_var_int_categorical_lab <- c("Gender", "Blood group", "Smoking level")
  
vec_var_int_continuous <- c('systbp', 'weight', 'weight_1year', 'height', 'abd_grith',
                            'hip_size', 'FT3', 'FT4', 'TSH', 'age')
vec_var_int_continuous_lab <- c('systolic blood pressure [mmHg]', 'weight [kg]', 'weight after 1 year [kg]', 'height [cm]', 'abdominal grith [cm]', 
                                'hip size [cm]', 'FT3', 'FT4', 'TSH', 'age [years]')
```



```{r, results = 'asis'}
# for loop for categorical parameters

for (j in 1:length(vec_var_int_categorical)) { 
# for (j in 1:3) {
   
   var_int <- vec_var_int_categorical[j]
   var_int_lab<- vec_var_int_categorical_lab[j]
 
   cat(knit_child("0_subRmds/subRmd_DAY1_ex4_categorical_SOLUTION_v20240223.Rmd"), sep = '\n')

 
  rm(var_int, var_int_lab)  
 }

``` 


```{r, results = 'asis'}
# for loop for continuous parameters

for (j in 1:length(vec_var_int_continuous)) { 
# for (j in 1:1) {
   
   var_int <- vec_var_int_continuous[j]
   var_int_lab<- vec_var_int_continuous_lab[j]
 
   cat(knit_child("0_subRmds/subRmd_DAY1_ex4_continuous_SOLUTION_v20240223.Rmd"), sep = '\n')

 
  rm(var_int, var_int_lab)  
 }

```






