---
title: "Day1 - Exercise 1 (SOLUTION)"
subtitle: "Example struma"
author: "YOUR NAME"
date: "`r Sys.Date()`"
output: 
   html_document:
     toc: TRUE
     toc_float: TRUE
---

```{r setup, include = FALSE}
# settings for output
  knitr::opts_chunk$set(echo = TRUE)

# Change setting of figure width and height
  knitr::opts_chunk$set(fig.width = ggplot2::unit(10, "cm"), fig.height = ggplot2::unit(8, "cm"))


# libraries used in this Rmd
  library(ggplot2)
  library(tidyverse)
  library(flextable)
  library(gtsummary)
```

```{r,  echo = FALSE, eval = TRUE}
# Load Rdata file
  filename <- list.files(path = "../Rdata/", pattern = "struma_prepared")

 load(file = paste0("../Rdata/", filename))

# show general information about dataset

 info$general %>% 
   flextable::flextable() %>% 
   flextable::font(., fontname = "Cambria (Textkörper)", part = "all") %>%
      flextable::fontsize(., size = 10 , part = "all") %>%
      flextable::padding(padding.top = 0,
                         padding.bottom = 0, part = "body") %>% 
  
      flextable::hline(.,
              border = officer::fp_border(color = "grey70", style = "dotted")) %>%
      # flextable::align(., j = 1, part = "all") %>%
      flextable::bg(., bg = "grey90", part = "header") %>% 
      flextable::bold(., bold = TRUE, part = "header") %>% 
      flextable::autofit()  

```



# Data set - struma

A goitre, or goiter, is a swelling in the neck resulting from an enlarged thyroid gland. 
[in German: goiter = Struma; goitre = Kropf].


In patients with goiter, a clinical study was conducted to investigate whether medication in addition to standard therapy (MED; yes/no) has an effect on thyroid hormones FT3, FT4 and TSH. 

The data set contains following parameters

```{r, results='asis', include = FALSE}
mylist <- names(dt_struma)
cat(paste("-", mylist), sep = "\n")
```


for `r nrow(dt_struma)`` patients.

```{r}
# TO DO: Show first few lines w/o weight_1year,  abd_grith, hip_size
 
 dt_struma %>% 
  select(-all_of(c("weight_1year", "abd_grith", "hip_size"))) %>% 
  filter(row_number() <6) %>% 
  flextable::flextable()

```

# Tables
## Descriptive statistics

**TO DO**

* Generate a table with descriptive statistics for all parameters separated by medication (MED)
   - look at homepage of gtsummary: https://www.danieldsjoberg.com/gtsummary/
   - tbl_summary()
      + look at arguments: 'included', 'by'
      + hint for 'included': use negative sign ,e.g., '-c(test)'
* Optional
   - make the parameter labels bold
   - add the spanning header 'Medication'
   - change for continuous parameters the statistic from 'median (IQR)' to 'mean (SD)'

```{r}
# table with descriptive statistics
 dt_struma %>%
  tbl_summary(include = -c(PatId),
              by = MED,
              statistic = list(where(is.numeric) ~  "{mean} ({sd})")) %>% 
  bold_labels() %>% 
  modify_spanning_header(
    update = starts_with("stat_") ~ "**Medication**") 


# alternative for selecting
  # dt_struma %>%
  #   select(-c(PatId)) %>% 
  #   tbl_summary(by = MED)
```

## Plots for descriptive statistics
### gender

**TO DO**

* generate an appropriate plot for gender separated by medication
    - use different colors for categories of medication
    - change legend position to the bottom
    

```{r}
# plot gender
ggplot(data = dt_struma,
       aes(x = gender, fill = MED)) +
  geom_bar(position=position_dodge()) +
    theme_bw() +
    theme(legend.position = "bottom") 
  
```

### age 
**TO DO**

* generate two different plots for age separated by medication
   - use different colors for categories of medication
   - change legend position to the bottom
   - hint: 'facet_grid()' is useful if you want automatized panels
* Optional
   - generate a quantile plot to investigate if age follows a normal distribution 
      + hint: geom_qq(), geom_qq_line()
   - change colors for the two medication categories to: #00AFBB and #E7B800

```{r}
# plot1 age
ggplot(data = dt_struma,
       aes(x = age, fill = MED)) +
  geom_boxplot() +
    theme_bw()+
    theme(legend.position = "bottom")
 
```


```{r}
# plot2 age
ggplot(data = dt_struma,
       aes(x = age, fill = MED)) +
  geom_histogram(color = "black") +
   theme_bw()+
   theme(legend.position = "bottom") +
  
  facet_grid(MED~.)
```

```{r}
# QQ plot age
ggplot(data = dt_struma,
       aes(sample = age, color = MED)) +
  geom_qq() +
  geom_qq_line() +
  
    xlab("Theoretical") +
    ylab("Sample") +
    scale_color_manual(values = c("#00AFBB", "#E7B800")) +
  theme_bw() +
  
  facet_grid(MED~.)


```


## Summary tables
**TO DO (optional)**

* Sometimes it is interesting to get summary information from your data, e.g., for each category of gender you want to know
   - how many observations
   - what is the minimum age and maximum age observed
   
```{r, eval = TRUE, echo = TRUE}
# summary table
  # use round() to have only 1 decimal place for the columns with age
  # use flextable() to get a nicer output

dt_struma %>%
  group_by(gender) %>% 
  summarize(n_total = n(),
            age_min = round(min(age),1 ),
            age_max = round(max(age),1)) %>% 
  flextable::flextable()

```
 

  
   


