---
title: "Day1 - Exercise 2 (SOLUTION)"
subtitle: "Example struma"
author: "YOUR NAME"
date: "`r Sys.Date()`"
output: 
   html_document:
     toc: TRUE
     toc_float: TRUE
---

```{r setup, include = FALSE}
# settings for output
  knitr::opts_chunk$set(echo = TRUE)

# Change setting of figure width and height
  knitr::opts_chunk$set(fig.width = ggplot2::unit(10, "cm"), fig.height = ggplot2::unit(8, "cm"))


# libraries used in this Rmd
  library(ggplot2)
  library(tidyverse)
  library(flextable)
  library(gtsummary)
  
  library(cowplot)
```

```{r,  echo = FALSE, eval = TRUE}
# Load Rdata file
  filename <- list.files(path = "../Rdata/", pattern = "struma_prepared")

 load(file = paste0("../Rdata/", filename))

# show general information about dataset

 info$general %>% 
   flextable::flextable() %>% 
   flextable::font(., fontname = "Cambria (Textkörper)", part = "all") %>%
      flextable::fontsize(., size = 10 , part = "all") %>%
      flextable::padding(padding.top = 0,
                         padding.bottom = 0, part = "body") %>% 
  
      flextable::hline(.,
              border = officer::fp_border(color = "grey70", style = "dotted")) %>%
      # flextable::align(., j = 1, part = "all") %>%
      flextable::bg(., bg = "grey90", part = "header") %>% 
      flextable::bold(., bold = TRUE, part = "header") %>% 
      flextable::autofit()  

```

Instead of working directly with the parameter names we want to work with 'placeholders'.


## Descriptive statistics - working with variables as placeholders
### gender
```{r, include = FALSE}
# bar plot - previous exercise

# ggplot(data = dt_struma,
#        aes(x = gender, fill = MED)) +
#   geom_bar(position=position_dodge()) +
#    scale_fill_manual(values = c("#00AFBB", "#E7B800")) +
#     theme_bw() +
#     theme(legend.position = "bottom")

```

**TO DO**

* use the bar plot for gender from the previous exercise and work with placeholders
   - don't forget to adapt the axis label and legend title
* create for gender a table with descriptive statistics using 'tbl_summary()' (separated by medication) and work with placeholders
* Optional - plot
   -  use also a placeholder for the colors (e.g., "#00AFBB", "#E7B800")
* Optional - table
   - make the parameter labels bold
   - add the spanning header 'Medication' using the placeholder

```{r}
# placeholders
var_int <- "gender"
var_int_lab <- "Gender"

group_int <- "MED"
group_int_lab <- "Medication"
group_int_colors <- c("#00AFBB", "#E7B800")

```





```{r}
# bar plot
ggplot(data = dt_struma,
       aes(x = get(var_int), fill = get(group_int))) +
  geom_bar(position=position_dodge()) +
    xlab(var_int_lab) +
    scale_fill_manual(name = group_int_lab,
                      values = group_int_colors) +
  
   
    theme_bw() +
    theme(legend.position = "bottom") 

  
```

```{r, warning = FALSE}
# table 
 dt_struma %>%
  tbl_summary(include = all_of(var_int),
              by = group_int) %>% 
  bold_labels() %>% 
  modify_spanning_header(
    update = starts_with("stat_") ~ paste0("**", group_int_lab, "**")) 

```

```{r}
# remove objects
rm(var_int, var_int_lab, group_int, group_int_lab, group_int_colors)
```


### age 
```{r, include = FALSE}
# plots from previous exercise

# boxplot ---

# ggplot(data = dt_struma,
#        aes(x = age, fill = MED)) +
#   geom_boxplot() +
#     theme_bw()+
#     theme(legend.position = "bottom")
#  

# histogramm ---
# ggplot(data = dt_struma,
#        aes(x = age, fill = MED)) +
#   geom_histogram(color = "black") +
#    theme_bw()+
#    theme(legend.position = "bottom") +
#   
#   facet_grid(MED~.)

# qq plot ---
# ggplot(data = dt_struma,
#        aes(sample = age, color = MED)) +
#   geom_qq() +
#   geom_qq_line() +
#   
#     xlab("Theoretical") +
#     ylab("Sample") +
#     scale_color_manual(values = c("#00AFBB", "#E7B800")) +
#   theme_bw() +
#   
#   facet_grid(MED~.)


```

**TO DO**

* use the box plot, histogram and qq-plot for age from the previous exercise and work with placeholders
   - don't forget to adapt the axis label and legend title
   - use function 'plot_grid' (package cowplot) to produce one plot with three panels
* create for age a table with descriptive statistics using 'tbl_summary()' (separated by medication) and work with placeholders
* Optional - plots
   - use also a placeholder for the colors for all plots
   - remove legends within the separate panels and give legend separately
      + 2x2 plot
      + panel A boxplot
      + panel B qq-plot
      + panel C histogram
      + panel D legend (no panel label) [hint: 'get_legend' (package cowplot)]
* Optional - table
   - try argument 'statistic' to display several statistics (median with IQR, range, mean with sd)
   - make the parameter labels bold
   - add the spanning header 'Medication' using the placeholder

```{r}
# placeholders
var_int <- "age"
var_int_lab <- "Age [years]"

group_int <- "MED"
group_int_lab <- "Medication"
group_int_colors <- c("#00AFBB", "#E7B800")

```




```{r}
# boxplot ---
p_boxplot <- 
  ggplot(data = dt_struma,
         aes(x = get(var_int), fill = get(group_int))) +
    geom_boxplot() +
    
    xlab(var_int_lab) +
    scale_fill_manual(values = group_int_colors,
                      name = group_int_lab) +
    
    
    theme_bw()+
    theme(legend.position = "bottom")

  
# histogramm ---
p_hist <-
  ggplot(data = dt_struma,
         aes(x = get(var_int), fill = get(group_int))) +
    geom_histogram(color = "black") +
  
      xlab(var_int_lab) +
      scale_fill_manual(values = group_int_colors,
                        name = group_int_lab) +
   
     theme_bw()+
     theme(legend.position = "bottom") +
 

    facet_grid(get(group_int)~.)

# qq plot ---
p_qqplot <-
  ggplot(data = dt_struma,
         aes(sample = get(var_int), color = get(group_int))) +
    geom_qq() +
    geom_qq_line() +
  
      xlab("Theoretical") +
      ylab("Sample") +
      scale_color_manual(values = group_int_colors,
                         name = group_int_lab) +
    theme_bw() +
  
    facet_grid(get(group_int)~.)

# one big plot with panels

pA <- p_boxplot + theme(legend.position = "none")
pC <- p_hist + theme(legend.position = "none")
pB <- p_qqplot + theme(legend.position = "none")


plegend <- cowplot::get_legend(p_boxplot)

cowplot::plot_grid(pA, pB, pC,plegend, nrow = 2, ncol = 2, labels = c("A", "B", "C", NA))

```




```{r, warning = FALSE}
# table
dt_struma %>%
  tbl_summary(include = all_of(c(var_int)),
              by = group_int,
              type = list(var_int ~ "continuous2"),
              statistic = list(all_continuous2() ~ c("{median} ({p25} - {p75})", 
                                                   "{min} - {max}",
                                                   "{mean} ({sd})"))) %>% 
  bold_labels() %>% 
   modify_spanning_header(
    update = starts_with("stat_") ~ paste0("**", group_int_lab, "**")) 

```


```{r}
# remove objects
rm(var_int, var_int_lab, group_int, group_int_lab, group_int_colors)
rm(p_hist, p_qqplot, p_boxplot, pA, pB, pC, plegend)
  
```

