---
title: "Day1 - Exercise 2 (SOLUTION)"
subtitle: "Example struma"
author: "YOUR NAME"
date: "`r Sys.Date()`"
output: 
   html_document:
     toc: TRUE
     toc_float: TRUE
---

```{r setup, include = FALSE}
# settings for output
  knitr::opts_chunk$set(echo = TRUE)

# Change setting of figure width and height
  knitr::opts_chunk$set(fig.width = ggplot2::unit(10, "cm"), fig.height = ggplot2::unit(8, "cm"))


# libraries used in this Rmd
  library(ggplot2)
  library(tidyverse)
  library(flextable)
  library(gtsummary)
  
  library(cowplot)
```

```{r,  echo = FALSE, eval = TRUE}
# Load Rdata file
  filename <- list.files(path = "../Rdata/", pattern = "struma_prepared")

 load(file = paste0("../Rdata/", filename))

# show general information about dataset

 info$general %>% 
   flextable::flextable() %>% 
   flextable::font(., fontname = "Cambria (Textkörper)", part = "all") %>%
      flextable::fontsize(., size = 10 , part = "all") %>%
      flextable::padding(padding.top = 0,
                         padding.bottom = 0, part = "body") %>% 
  
      flextable::hline(.,
              border = officer::fp_border(color = "grey70", style = "dotted")) %>%
      # flextable::align(., j = 1, part = "all") %>%
      flextable::bg(., bg = "grey90", part = "header") %>% 
      flextable::bold(., bold = TRUE, part = "header") %>% 
      flextable::autofit()  

```

Instead of working directly with the parameter names we want to work with 'placeholders'.


## Descriptive statistics - working with variables as placeholders
### gender
```{r, include = FALSE}
# bar plot - previous exercise

# ggplot(data = dt_struma,
#        aes(x = gender, fill = MED)) +
#   geom_bar(position=position_dodge()) +
#    scale_fill_manual(values = c("#00AFBB", "#E7B800")) +
#     theme_bw() +
#     theme(legend.position = "bottom")

```

**TO DO**

* use the bar plot for gender from the previous exercise and work with placeholders
   - don't forget to adapt the axis label and legend title
* create for gender a table with descriptive statistics using 'tbl_summary()' (separated by medication) and work with placeholders
* Optional - plot
   -  use also a placeholder for the colors (e.g., "#00AFBB", "#E7B800")
* Optional - table
   - make the parameter labels bold
   - add the spanning header 'Medication' using the placeholder

```{r}
# placeholders


```





```{r}
# bar plot


  
```

```{r, warning = FALSE}
# table 


```




### age 
```{r, include = FALSE}
# plots from previous exercise

# boxplot ---

# ggplot(data = dt_struma,
#        aes(x = age, fill = MED)) +
#   geom_boxplot() +
#     theme_bw()+
#     theme(legend.position = "bottom")
#  

# histogramm ---
# ggplot(data = dt_struma,
#        aes(x = age, fill = MED)) +
#   geom_histogram(color = "black") +
#    theme_bw()+
#    theme(legend.position = "bottom") +
#   
#   facet_grid(MED~.)

# qq plot ---
# ggplot(data = dt_struma,
#        aes(sample = age, color = MED)) +
#   geom_qq() +
#   geom_qq_line() +
#   
#     xlab("Theoretical") +
#     ylab("Sample") +
#     scale_color_manual(values = c("#00AFBB", "#E7B800")) +
#   theme_bw() +
#   
#   facet_grid(MED~.)


```

**TO DO**

* use the box plot, histogram and qq-plot for age from the previous exercise and work with placeholders
   - don't forget to adapt the axis label and legend title
   - use function 'plot_grid' (package cowplot) to produce one plot with three panels
* create for age a table with descriptive statistics using 'tbl_summary()' (separated by medication) and work with placeholders
* Optional - plots
   - use also a placeholder for the colors for all plots
   - remove legends within the separate panels and give legend separately
      + 2x2 plot
      + panel A boxplot
      + panel B qq-plot
      + panel C histogram
      + panel D legend (no panel label) [hint: 'get_legend' (package cowplot)]
* Optional - table
   - try argument 'statistic' to display several statistics (median with IQR, range, mean with sd)
   - make the parameter labels bold
   - add the spanning header 'Medication' using the placeholder

```{r}
# placeholders


```




```{r}
# boxplot ---


  
# histogramm ---



# qq plot ---


# one big plot with panels




```
```{r, warning = FALSE}
# table
 

```




